A Detection of the Environmental Dependence of the Stellar Profiles and Halos of Massive Central Galaxies

### 2017-03-31 draft/paper1.tex
Change short title

%% ------------------------------------------------------------------------------------ %% 
\title[Structure and Halo of Massive Galaxies]{Tracing the Stellar Halo of Massive 
       Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam}

>>>>

%% ------------------------------------------------------------------------------------ %% 
\title[Mass Dependent Stellar Halo in Massive Galaxies]{Tracing the Stellar Halo of 
	   Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam}

### 2017-03-31 draft/paper2.tex
Change short title

%% ------------------------------------------------------------------------------------ %% 
\title[Structure and Halo of Massive Galaxies]{A Detection of the Environmental 
       Dependence of the Stellar Profiles and Halos of Massive Central Galaxies}

>>>>

%% ------------------------------------------------------------------------------------ %% 
\title[Structure and Environment of Massive Galaxies]{A Detection of the Environmental 
       Dependence of the Stellar Profiles and Halos of Massive Central Galaxies}
